\Title

### 2013-03-12 synmut.tex
Author summary

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\comment{to be written\dots}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the Author Summary between 150 and 200 words
% Use first person.   
\section*{Author Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Human Immunodeficiency Virus (HIV) epidemic is a plague of our era. The
main reason why it is so hard to treat is that, althought one single strain of
the virus is transmitted, many variants appear quickly within the same patient
by random mutation. Among all mutations, synonymous ones do not change the amino
acid sequence of the viral proteins and are often assumed to be of no
evolutionary consequence. In this article, we show that many synonymous
mutations imply a slight fitness cost for the virus; this cost is
linked to the preservation of certain base pairs in the single-stranded HIV RNA.
We argue that deleterious synonymous mutations can be widespread within an HIV
infection, despite their cost and for a limited time only, if they arise by
chance on a very efficient virus. Furthermore, we suggest that even the most
efficient virus has only a small chance of eventually dominate, because
(i) it must often compete with incompatible and equally efficient variants, and
(ii) the host immune systems soon develops countermeasures.
